A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-05-20 plots/combined/aft_comparison.tex
update image references
update plots
Updates from Overleaf
clean bibliography

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{lrrrrrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -5810.78 & 0.84 & 0.84 & -5810.78 & 2.08 & 0.65 \\
log_logistic & -6204.80 & 0.85 & 0.84 & -6204.80 & 0.23 & 0.17 \\
log_normal & -6076.91 & 0.84 & 0.84 & -6076.91 & 0.17 & 0.15 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the Combined dataset. The metrics are defined in Sec.~\ref{afr}}
\label{tab:combined}
\begin{tabular}{lrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -5.57e+03 & -5.57e+03 & 0.84 & 0.84 & 0 & 0 \\
Log Logistic & -5.71e+03 & -5.71e+03 & 0.85 & 0.84 & 0.01 & 0 \\
Log Normal & -5.85e+03 & -5.85e+03 & 0.84 & 0.84 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
